\chapter*{Acknowledgements}

I am very lucky to be able to say that I have honestly enjoyed almost every second (thesis writing notwithstanding!) of my PhD.
The fact that I can say this is down entirely to the wonderful people I have had the pleasure of spending time with over the last four years.

My thanks go first to my supervisors, David Ham and Jack Betteridge.
Their support and expertise offered throughout the PhD has been invaluable, and without it there is no way I would have achieved the same amount that I have as cheerfully as I have.

I would also like to thank my colleagues in the core Firedrake team, both past and present: Koki, Daiane, Nacime, Reuben, and Sophia, for their helpfulness and companionship.
As is often said, it is Firedrake's community that makes it so special and that was certainly my experience.
I really appreciate getting the opportunity to work with you all.
A special mention is also needed for former core team member Lawrence Mitchell for suggesting that I apply to do this PhD.
Without you this would never have happened.

Further thanks are due to the wonderful group of friends that I have shared an office with through my PhD: Thivan, Sara, Jamie, Karina, Henry, and Maria.
I cannot believe I was somehow put in the friendliest office in all of Huxley and I count myself very lucky to have gotten to know you all.

Lastly my biggest thanks of all go to my family for their unwavering support throughout this journey.
In particular, Rhiannon has been nothing short of amazing.
By now she has heard more about my `trees and triangles' than anyone else and yet she still puts up with me!

\clearpage
